Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-04-17 paper.qmd
HTML
Update paper

@@

```{r}
#| label: tbl-tools
# For PDF:
knitr::kable(tools, caption = "Summary of existing tools for estimating cycling potential.", booktabs = TRUE) |>
  kableExtra::kable_styling(latex_options = "striped", full_width = FALSE) |>
  kableExtra::column_spec(1, width = "13em") |>
  kableExtra::column_spec(2, width = "15em") |>
  kableExtra::column_spec(3, width = "12em") |>
  kableExtra::column_spec(4, width = "5em")
# For HTML:
# knitr::kable(tools, caption = "Summary of existing tools for estimating cycling potential.")
```

@@

```{r}
#| label: tbl-trip-purposes
#| tbl-cap: "Trip purposes used in the CRUSE Tool."
# For PDF:
knitr::kable(trip_purposes, booktabs = TRUE) |>
  kableExtra::kable_styling(latex_options = "striped", full_width = FALSE, font_size = 8) |>
  kableExtra::column_spec(1, width = "5em") |>
  kableExtra::column_spec(2, width = "12em") |>
  kableExtra::column_spec(3, width = "15em") |>
  kableExtra::column_spec(4, width = "15em")
# For HTML:
# knitr::kable(trip_purposes, caption = "Trip purposes used in the CRUSE Tool.")
```

>>>>

Note: preprint now available here: https://osf.io/preprints/osf/a72yh

Please cite as

Lovelace, Robin, Joey Talbot, Eugeni Vidal-Tortosa, Hussein Mahfouz, Elaine Brick, Peter Wright, Gary O'Toole, et al. 2024. “Cycle Route Uptake and Scenario Estimation (CRUSE): An Approach for Developing Strategic Cycle Network Planning Tools.” OSF Preprints. March 29. doi:10.31219/osf.io/a72yh.

@@

```{r}
#| label: tbl-tools
# # For PDF:
# knitr::kable(tools, caption = "Summary of existing tools for estimating cycling potential.", booktabs = TRUE) |>
#   kableExtra::kable_styling(latex_options = "striped", full_width = FALSE) |>
#   kableExtra::column_spec(1, width = "13em") |>
#   kableExtra::column_spec(2, width = "15em") |>
#   kableExtra::column_spec(3, width = "12em") |>
#   kableExtra::column_spec(4, width = "5em")
# For HTML:
knitr::kable(tools, caption = "Summary of existing tools for estimating cycling potential.")
```

@@

```{r}
#| label: tbl-trip-purposes
#| tbl-cap: "Trip purposes used in the CRUSE Tool."
# For PDF:
# knitr::kable(trip_purposes, booktabs = TRUE) |>
#   kableExtra::kable_styling(latex_options = "striped", full_width = FALSE, font_size = 8) |>
#   kableExtra::column_spec(1, width = "5em") |>
#   kableExtra::column_spec(2, width = "12em") |>
#   kableExtra::column_spec(3, width = "15em") |>
#   kableExtra::column_spec(4, width = "15em")
# For HTML:
knitr::kable(trip_purposes, caption = "Trip purposes used in the CRUSE Tool.")
```
